Precise Weed and Maize classification through Convolutional Neuronal Networks

### 2017-07-06 PaperBCJ.tex
cambio
abstrac

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Today the computation stays i 
\end{abstract}

@@

\section{Introduction}
% no \IEEEPARstart

% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill August 26, 2015

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

@@

For this stage, we considered an extra dataset with 200 images of maize plants and 203 images of weed, the results were comparated between cNET with 64 and 16 filters, each one would be  
\begin{table}[h!]
\centering
\begin{tabular}{|l|c|c|c|} 
 \hline
 \multicolumn{4}{ |c| }{GPU} \\
 \hline
   & \% Accuracy Weed & \% Accuracy Maize  & Average time of classification   \\ 
 \hline 
 cNET(64 Filters) & 81.6 & 88.36 & 2.34 ms  \\ [0.75ex]
 \hline
 cNET(16 Filters) & 85.71 & 87.13 & 951  $\mu$ s \\ [0.75ex]
  \hline
 \multicolumn{4}{ |c| }{CPU} \\
 \hline
   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification \\ 
 \hline 
 cNET(64 Filters) & 81.6 & 88.36 & 51.6 ms  \\ [0.75ex]
 \hline
 cNET(16 Filters) & 85.71 & 87.13 & 17.23 ms \\ [0.75ex]
  \hline
 \multicolumn{4}{ |c| }{CPU Raspberry Pi 3} \\
 \hline
   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification\\ 
 \hline 
 cNET(64 Filters) & 81.6 & 88.36 & 615 ms  \\ [0.75ex]
 \hline
 cNET(16 Filters) & 85.71 & 87.13 & 161 s \\ [0.75ex]
  \hline
\end{tabular}
\caption{Test}
\label{table:2}
\end{table}

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{Suarez:Pinero}
R. ~Su\'arez, J. ~Pi\~neiro and J. ~Valladares \emph{Distintos Sistemas De Escarda En Ma\'iz Forrajero} . Vol ~II. \hskip 1em plus
  0.5em minus 0.4em\relax Gij\'on , Spain: Publicaciones SERIDA, 2005. Web. 3 Mar. 2017.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Deep Learning has played a very important role in modern times, being very used in artificial vision and especially in pattern recognition, which opens many doors in the fields of application among which is agriculture of presicion. In this paper we present the study of a convolutional neural network applied to the classification of plants of maize and weeds in real time, directed to fields of maize in its initial stage. The algorithm has two stages, segmentation of images and classification. In the segmentation it is sought to separate from the image the plants individually. While the classification is given through the convolutional neural network, previously trained with a dataset generated through the segmentation stage.The performance of the network is illustrated by analysis and comparisons with different network architectures, then with the network that presented better results, we experimented by modifying its number of filters, to analyze their behavior. Finally, the resulting network was tested on different processors to compare classification times.\\
\end{abstract}

@@

@@

For this stage, we considered an extra dataset with 200 images of maize plants and 203 images of weed, the results were comparated between cNET with 64 and 16 filters, each one would be  
\begin{table}[h!]
\centering
\begin{tabular}{|l|c|c|p{2cm}|}  
 \hline
 \multicolumn{4}{ |c| }{GPU} \\
 \hline
   cNET & \% Accuracy Weed & \% Accuracy Maize  & Average time of classification   \\ 
 \hline 
 64 Filters & 81.6 & 88.36 & 2.34 ms  \\ [0.75ex]
 \hline
 16 Filters & 85.71 & 87.13 & 951  $\mu$ s \\ [0.75ex]
  \hline
 \multicolumn{4}{ |c| }{CPU} \\
 \hline
   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification \\ 
 \hline 
 64 Filters & 81.6 & 88.36 & 51.6 ms  \\ [0.75ex]
 \hline
 16 Filters & 85.71 & 87.13 & 17.23 ms \\ [0.75ex]
  \hline
 \multicolumn{4}{ |c| }{CPU Raspberry Pi 3} \\
 \hline
   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification\\ 
 \hline 
 64 Filters & 81.6 & 88.36 & 615 ms  \\ [0.75ex]
 \hline
 16 Filters & 85.71 & 87.13 & 161 s \\ [0.75ex]
  \hline
\end{tabular}
\caption{Test}
\label{table:2}
\end{table}

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
%\bibliographystyle{IEEEtran}
%\bibliography{/home/mauricio/PaperIEEE/ref.bib}

\begin{thebibliography}{1}

%\bibliographystyle{IEEEtran}
%\bibliography{/home/mauricio/PaperIEEE/ref.bib}
%\bibitem{ref}
\bibitem{Suarez:Pinero}
R. ~Su\'arez, J. ~Pi\~neiro and J. ~Valladares \emph{Distintos Sistemas De Escarda En Ma\'iz Forrajero} . Vol ~II. \hskip 1em plus
  0.5em minus 0.4em\relax Gij\'on , Spain: Publicaciones SERIDA, 2005. Web. 3 Mar. 2017.
